Screening Sinkhorn Algorithm for Regularized Optimal Transport

### 2019-05-19 tex/v3/appendix.tex
expe

>>>>

\subsection{Additional experimental results}

\begin{figure*}[t]
	\centering

	\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl1.pdf}
	\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl10.pdf}
	\includegraphics[width=6.cm]{../../figure/da_accur_toy_regcl1.pdf}
	\includegraphics[width=6.cm]{../../figure/da_accur_toy_regcl10.pdf}
	\caption{OT Domain adaptation : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
	\label{fig:otda}
\end{figure*}

### 2019-05-19 tex/v3/section_5_numeric_expes.tex
new
expe

In this subsection, we analyse the impact of using \emph{Screenkhorn}
instead of Sinkhorn in a complex machine learning pipeline. Our two applications
are a dimensionality reduction technique, denoted as Wasserstein Discriminant Analysis (WDA), based on Wasserstein distance approximated
through Sinkhorn divergence \cite{flamary2018WDA} and a domain-adaptation using optimal transport mapping \cite{courty2017optimal}, named OTDA. For both applications, we have based our code
on the ones of POT \cite{flamary2017pot} and just replaced the Sinkhorn function call with a Screenkhorn one. We have considered the POT's default Sinkhorn stopping criterion parameters and for Screenkhorn, the LBFGS algorithm is stopped when the 
largest component of the projected gradient is smaller than $10^{-9}$, when the
number of iterations of number of objective function evaluations reach $10^{6}$.

@@

	\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl1.pdf}
	\includegraphics[width=6.cm]{../../figure/da_gain_mnist_regcl1.pdf}
	\caption{OT Domain adaptation : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
	\label{fig:otda}
\end{figure*}

>>>>

In this subsection, we analyse the impact of using \emph{Screenkhorn}
instead of Sinkhorn in a complex machine learning pipeline. Our two applications
are a dimensionality reduction technique, denoted as Wasserstein Discriminant Analysis (WDA), based on Wasserstein distance approximated
through Sinkhorn divergence \cite{flamary2018WDA} and a domain-adaptation using optimal transport mapping \cite{courty2017optimal}, named OTDA. For both applications, we have based our code
on the ones of POT \cite{flamary2017pot} and just replaced the Sinkhorn function call with a Screenkhorn one. We have considered the POT's default Sinkhorn stopping criterion parameters and for Screenkhorn, the LBFGS algorithm is stopped when the 
largest component of the projected gradient is smaller than $10^{-6}$, when the
number of iterations of number of objective function evaluations reach $10^{5}$. For all
applications, we have set $\eta=1$.

@@

	\includegraphics[width=6.cm]{../../figure/da_gain_mnist_regcl1.pdf}
	\includegraphics[width=6.cm]{../../figure/da_gain_mnist_regcl10.pdf}
	\caption{OT Domain adaptation : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
	\label{fig:otda}
\end{figure*}
